---
title: "Our Team"
---

```{r setup}
#| include: false
library(readr)
library(dplyr)
library(glue)
```

Our work on the **POPCORN-NCD Reporting Guideline** is led by an international collaborative group committed to transparency and rigour in simulation-modelling research.

---

## Leads

<!--
COORDINATOR: Leadership section is MANUAL - use the template below to add new co-investigators.
Copy the entire block between the ::: {.team-member} divs and paste below, then fill in the details.
-->

::: {.team-grid}

::: {.team-member}

**Douglas Manuel, MD MSc FRCPC**

*The Ottawa Hospital Research Institute; University of Ottawa*

Ottawa, Canada

**Expertise:** Population health microsimulation modelling; model validation methodology; chronic disease epidemiology; reporting guideline development.


**Role:** Principal Investigator responsible for overall project management, coordination of working groups, stakeholder engagement, and oversight of the consensus process and guideline development.

[{{< fa envelope >}} dmanuel@ohri.ca](mailto:dmanuel@ohri.ca) | [{{< fa brands orcid >}} ORCID](https://orcid.org/0000-0002-0599-2061)

:::

::: {.team-member}

**Oliver Mytton, MD MPH**

*UCL Great Ormond Street Institute for Child Health; Milton Keynes City Council*

London, United Kingdom

**Expertise:** Public health simulation modelling; population health intervention evaluation; reporting guideline development.

**Role:** Co-Principal Investigator responsible for guideline methodology, evidence synthesis, Delphi process coordination, and alignment with EQUATOR Network standards.

[{{< fa brands orcid >}} ORCID](https://orcid.org/)

:::

::: {.team-member}

**Tony Blakely, MBChB MPH PhD FAFPHM**

*University of Melbourne; Institute for Health Metrics and Evaluation*

Melbourne, Australia

**Expertise:** NCD simulation modelling; causal inference methods; health economic evaluation; population intervention research; simulation frameworks.

**Role:** Chair of the Strategic Advisory Committee, responsible for leading the Committee, synthesizing consensus, and ensuring diverse international perspectives inform guideline development and implementation strategies.

[{{< fa brands orcid >}} ORCID](https://orcid.org/0000-0002-2096-829X)

:::

:::

---

## Strategic Advisory Group

<!--
COORDINATOR: SAG is AUTO-GENERATED from data/team-members.csv

To add/update members:
1. Open Google Sheet with team member responses
2. Download/copy rows where Section = "SAG"
3. Upload to data/team-members.csv (or edit directly in GitHub)
4. Commit the CSV file - site will rebuild automatically

CSV Columns needed: Section, Name, Credentials, Institution, Country, Expertise, ORCID, Email, Photo
-->

Our Strategic Advisory Group (SAG) provides expert guidance on the development and implementation of POPCORN-NCD reporting guidelines. Members represent diverse geographical regions, methodological expertise, and stakeholder perspectives.

```{r}
#| echo: false
#| output: asis

# Read team data
team <- read_csv("data/team-members.csv", show_col_types = FALSE)

# Filter for SAG
sag <- team %>% filter(Section == "SAG")

if (nrow(sag) > 0) {
  cat('::: {.team-grid}\n\n')

  for (i in 1:nrow(sag)) {
    # Start card
    cat('::: {.team-member}\n\n')

    # Photo (if provided)
    if (!is.na(sag$Photo[i]) && sag$Photo[i] != "") {
      cat(glue('![{sag$Name[i]}]({sag$Photo[i]}){{.img-circle width="100"}}\n\n'))
    }

    # Name and credentials
    cat(glue('**{sag$Name[i]}'))
    if (!is.na(sag$Credentials[i]) && sag$Credentials[i] != "") {
      cat(glue(', {sag$Credentials[i]}'))
    }
    cat('**\n\n')

    # Institution
    cat(glue('*{sag$Institution[i]}*\n\n'))

    # Country
    if (!is.na(sag$Country[i]) && sag$Country[i] != "") {
      cat(glue('{sag$Country[i]}\n\n'))
    }

    # Expertise
    if (!is.na(sag$Expertise[i]) && sag$Expertise[i] != "") {
      cat(glue('**Expertise:** {sag$Expertise[i]}\n\n'))
    }

    # ORCID
    if (!is.na(sag$ORCID[i]) && sag$ORCID[i] != "") {
      cat(glue('[{{{{< fa brands orcid >}}}} ORCID](https://orcid.org/{sag$ORCID[i]})\n\n'))
    }

    # End card
    cat(':::\n\n')
  }

  cat(':::\n\n')
} else {
  cat('*Members to be announced.*\n\n')
}
```

---

## Working Group

<!--
COORDINATOR: Working Group is AUTO-GENERATED from data/team-members.csv

To add/update members:
1. Open Google Sheet with team member responses
2. Download/copy rows where Section = "Working Group"
3. Upload to data/team-members.csv (or edit directly in GitHub)
4. Commit the CSV file - site will rebuild automatically

CSV Columns needed: Section, Name, Credentials, Institution, Country, Expertise, ORCID, Email, Photo
-->

Our working group includes researchers, methodologists, and knowledge users who contribute to the development of the POPCORN-NCD reporting guidelines.

```{r}
#| echo: false
#| output: asis

# Read team data
team <- read_csv("data/team-members.csv", show_col_types = FALSE)

# Filter for Working Group
wg <- team %>% filter(Section == "Working Group")

if (nrow(wg) > 0) {
  cat('::: {.team-grid}\n\n')

  for (i in 1:nrow(wg)) {
    # Start card
    cat('::: {.team-member}\n\n')

    # Photo (if provided)
    if (!is.na(wg$Photo[i]) && wg$Photo[i] != "") {
      cat(glue('![{wg$Name[i]}]({wg$Photo[i]}){{.img-circle width="100"}}\n\n'))
    }

    # Name and credentials
    cat(glue('**{wg$Name[i]}'))
    if (!is.na(wg$Credentials[i]) && wg$Credentials[i] != "") {
      cat(glue(', {wg$Credentials[i]}'))
    }
    cat('**\n\n')

    # Institution
    cat(glue('*{wg$Institution[i]}*\n\n'))

    # Country
    if (!is.na(wg$Country[i]) && wg$Country[i] != "") {
      cat(glue('{wg$Country[i]}\n\n'))
    }

    # Expertise
    if (!is.na(wg$Expertise[i]) && wg$Expertise[i] != "") {
      cat(glue('**Expertise:** {wg$Expertise[i]}\n\n'))
    }

    # ORCID
    if (!is.na(wg$ORCID[i]) && wg$ORCID[i] != "") {
      cat(glue('[{{{{< fa brands orcid >}}}} ORCID](https://orcid.org/{wg$ORCID[i]})\n\n'))
    }

    # End card
    cat(':::\n\n')
  }

  cat(':::\n\n')
} else {
  cat('*Members to be announced.*\n\n')
}
```

---

## Acknowledgement

This work is supported by [Funder names to be added].

All team members have completed conflict of interest disclosures, available upon request by contacting [dmanuel@ohri.ca](mailto:dmanuel@ohri.ca).

---

*Interested in joining our team? Contact us at [dmanuel@ohri.ca](mailto:dmanuel@ohri.ca).*
